### 2021-03-04 papers/jin-thesis/Chapters/1Introduction.tex
A lot of thesis progress !

Cells are complicated. They have the ability to move, perfectly divide, and spatially organize themselves but are also responsible for fatal diseases when these functions fail. Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information to different parts of the cell. They travel around the cell on a cytoskeleton composed of microtubules that act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})). These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}). Because of kinesin and myosin's compact structure being close to the microtubule, they exhibit a uniform ``hand-over-hand" stepping pattern where their legs take turns alternating steps like a human. On the other hand, dynein's structure involves two autonomous motors that cause inconsistent steps. Dynein exhibits an inchworm pattern while walking where one leg consistently stays ahead of the other, emulating a limping motion.

@@

Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains. Figure (\ref{fig:structure}) displays these as the tail, the AAA+ rings (or motor), and the microtubule binding domain. The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/dynein_on_MT.png}
	\caption[Structure of Dynein]{\textbf{Structure of Dynein.} Illustration of cytoplasmic dynein's heavy chain subunits bounded to the microtubule. The AAA+ rings block the view of the independent linkers connecting to the tail. This rendition depicts dynein’s structure as a domain-rod system. \cite{TheTrappistArt}}
	\label{fig:structure}
\end{figure}

Dynein's physical structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature. Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring. In kinesin and myosin, the motor domains are much closer to the MT, causing a more controlled and consistent step due to their low center of mass. Despite dynein's large structure, it can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, which is why the AAA+ domains are referred to as the motor domains.

@@

Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis. The ATP binds to the motor domain and converts chemical energy into mechanical energy for the dynein to transition between different conformational states (physicial arrangements) during a step. This process allows the binding domains to let go and reattach to the microtubule at different locations causing varying step sizes. To measure dynein's step length, an axis is defined on the microtubule for where dynein can step.

The on-axis is defined to be parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is perpendicular, as shown in Figure (\ref{fig:axis}). Figure (\ref{fig:axis}) also displays the alternating helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\columnwidth]{Figures/Onaxis.png}
	\caption[Stepping Axis]{\textbf{Stepping axis.} Birds-eye view of the microtubule with the green areas identifying the microtubule binding domains. For the on-axis, positive displacement is defined towards the minus end of the microtubule. Dark grey and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers. \cite{Dewitt2012} }
	\label{fig:axis}
\end{figure}

@@

Here, affinity refers to the tendency and strength of the binding domain binding to the microtubule - high affinity being a secure attachment to the microtubule and low affinity being loose. The cycle utilizes the conformational transition between high and low affinity to explain dynein's unbinding and rebinding process. This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward. This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step. A closer visualization of this transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.

@@

Experimental research investigates the correlations within dynein's step and how different parameters may affect the pattern. These consist of the angle dependency during the stretching of the linker, the effect of the initial domain distance before the step, the ATP concentration for hydrolysis, etc. However, due to dynein's small scale, experiment often disagrees with one another and differs depending on the measuring technique.

@@

Experimentalists approach measuring dynein in various ways, which involve electron microscopy or quantum measuring techniques. Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod. Despite the different procedures, all measuring techniques suffer from their inability to measure steps within $\sim 0.4$ nm of where the binding domain lifted off. This causes short step lengths, where the binding domain quickly rebinds after unbinding, to be undetectable. The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables. In this paper, we will focus on Yildiz et al. unique finding of observing a stepping correlation between the initial interhead separation and step length.

@@

Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step. However, in 2012, Yildiz et al. observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}. This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping. Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.

@@

We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results. Currently, other simulations that model dynein's step exist, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle. These simulations suffer from numerous assumptions made about the physical aspects of dynein's step. (\textit{Should reference a simulation here}) Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame. These limitations make it impossible for the models to replicate unique discoveries about dyneins stepping, such as Yildiz's correlation from above.

To bridge this gap, Roundy et al. constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment. Instead of making assumptions about the physical properties of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes that the energy transfer from the ATP is incorporated within the binding processes. Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experiences Brownian motion during a step to mimic stochastic movement \cite{Capek2017, }. They were able to track dynein's precise movement along a walk and compare their stepping results to experiment. However, their simulation suffered from immense computaiton time and lacked the ability to optimize model parameters for a better fit to experiment. For this work, we will use their simulation as a foundation and implement a Monte Carlo method for reproducing data fast and generating an ensemble of statistics. We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism. More specifically, we want reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.

>>>>

Cells are complicated. They have the ability to move, perfectly divide, and spatially organize themselves but are also responsible for fatal diseases when these functions fail. Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track. These microtubules form the cytoskeleton in the cell and act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})). These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}). Because of kinesin and myosin's compact structure being close to the microtubule, they exhibit a uniform ``hand-over-hand" stepping pattern where their legs take turns alternating steps like a human. On the other hand, dynein's structure involves two autonomous motors that cause inconsistent steps. Dynein exhibits an inchworm pattern while walking where one leg consistently stays ahead of the other, emulating a limping motion.

@@

Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains. Figure (\ref{fig:structure}) displays these as the tail, the AAA+ rings (or motor), and the microtubule binding domain. The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks. Both lengths measuring greater than 20 nm in length causing dynein to stand up to 50 nm high.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/dynein_on_MT.png}
	\caption[Structure of Dynein]{\textbf{Structure of Dynein.} Illustration of cytoplasmic dynein's heavy chain subunits bounded to the microtubule. The AAA+ rings block the view of the linkers connecting them to the tail. For simplicity, this rendition depicts dynein’s structure as a domain-rod system. \cite{TheTrappistArt}}
	\label{fig:structure}
\end{figure}

Dynein's physical structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature. Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are a factor of a half larger than the diameter of the AAA+ ring. In kinesin and myosin, the motor domains are much closer to the MT, causing a more controlled and consistent step due to their low center of mass. Despite dynein's large structure, it can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, which is why the AAA+ domains are referred to as the motor domains.

@@

Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis. The ATP binds onto the motor domain and converts chemical energy into mechanical energy for the dynein to transition between different conformational states (physicial arrangements) during a step. This process allows the binding domains to unbind and reattach at different locations on the microtubule and thus, permit varying step sizes. To measure dynein's step, an axis is defined on the microtubule.

The on-axis is defined parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is perpendicular, as shown in Figure (\ref{fig:axis}). Figure (\ref{fig:axis}) also displays the alternating helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\columnwidth]{Figures/Onaxis.png}
	\caption[Stepping Axis]{\textbf{Stepping axis.} Birds-eye view of the microtubule with the green areas identifying the microtubule binding domains. For the on-axis, positive displacement is defined towards the minus end of the microtubule. Dark grey and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers, which are on average 8 nm apart in the on-axis. \cite{Dewitt2012} }
	\label{fig:axis}
\end{figure}

@@

Here, affinity refers to the tendency and strength of the domain binding to the microtubule - high affinity being a secure attachment to the microtubule, while low affinity is more relaxed. The cycle utilizes the conformational transitions between high and low affinity to explain dynein's unbinding and rebinding process. This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward. This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step. A closer visualization of this transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.

@@

Experimental research investigates the correlations within dynein's step and how different parameters may affect the pattern. These consist of the angle dependency during the stretching of the linker, the effect of the initial domain distance before the step, the ATP concentration for hydrolysis, etc. However, due to dynein's small scale, experiment often disagrees with one another and differ depending on the various measuring techniques.

@@

Experimentalists measures dynein in various ways that utilizes electron microscopy and quantum measuring devices. Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod. Despite the different procedures, all measuring techniques suffer from their inability to measure steps within $\sim 0.4$ nm of where the binding domain lifted off. This causes short step lengths, where the binding domain quickly rebinds after unbinding, to be undetectable. The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables. In this paper, we focus on Yildiz et al. unique observation of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping.

@@

Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step. However, in 2012, Yildiz et al. observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}. This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping. Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression, where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.

@@

We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results. Currently, other simulations that model dynein's step exist, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle. These simulations suffer from numerous assumptions made about the physical aspects of dynein's step. (\textit{Should reference a simulation here}) Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame. These limitations make it impossible for their models to replicate mechanical phenomenon observed in dynein's stepping, such as Yildiz's correlation from above.

To bridge this gap, Roundy et al. constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment. Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes. Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experienced Brownian motion to mimic stochastic movement \cite{Capek2017, }. They were able to track dynein's precise movement along a walk and compare their stepping results to experiment. However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbinded while $>20$ ms binded). Because of this, their simulation suffered from immense computaiton time and lacked the ability to optimize model parameters for a better fit to experiment. For this work, we will use their simulation as a foundation but replace the dynamical bounded state with a Monte Carlo algorithm. This allows us to only simulate the stepping motion, as the Monte Carlo will initially test equilibrium configurations before the step. This new method will drastically shorten computation time and generate larger ensembles of statistics. We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism. More specifically, we want reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.

### 2021-03-04 papers/jin-thesis/Chapters/2Theory.tex
A lot of thesis progress !

Despite dynein's complexity allowing its step to vary in both length and direction, we limit our model to one direction to eliminate the off-axis dimension when analyzing the forward stepping pattern of dynein. This would also simplify the asymmetry of the microtubule when the dynein is stepping either on the $\alpha$ or $\beta$ tubulin. We also simplify the stalk and linker to be massless because we are assuming the drag force to be much larger than the mass of the rods and domains. The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics. Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains slightly larger than experimental measurements.

\subsection{Domains as Angular Springs}
To best simulate the stretching and forward kicking motion of the power stroke, we define the domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ for each domain. This can be analogous to how humans walk, where the domains correspond to flexible joints when taking a step. Defining the domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law: 
\begin{equation}
    F_i=-c_i(\theta_i-\theta_{i,eq})
\end{equation}
where $c_i$ is the spring constant, $\theta_i$ is angle corresponding to the $i^{th}$ domain, and $\theta_{i,eq}$ is the equilibrium angle in which biases the motion. Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
\begin{equation} \label{eqn:energy}
    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
\end{equation}
%Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e. $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains. 
This equation is used throughout the simulation to determine the total energy of our dynein at a given conformation.

\subsection{Two-State System}
According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step. However, many of these states possess similar conformations, where the dynein either has one foot bounded while the other diffuses above the microtubule or has both feet bounded to the microtubule. Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.

@@

Similar to other simulations, the binding and unbinding process is governed by a rate-limiting step, where each process is associated with binding rates. These binding rates are model parameters defined by binding constants with units of probability per time. When the dynein is in the one bound state, the binding domain depends on two rebinding rates: the linker priming rate ($\rho_p$) and the binding rate ($\rho_b$). We assume that the unbound binding domain can only bind when the linker is primed and the unbound binding domain is within a vertical range of the microtubule, i.e.
\begin{equation}
	\rho_p=k_p
\end{equation}
\begin{equation}
	\rho_b=k_b(1-H(r_{ub,y}-\epsilon)).
\end{equation} 
Here, the $k_p$ is the priming rate constant, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.

@@

To favor trailing steps, we define an angle dependent exponential factor within the binding domains and mathematically express this as,
\begin{equation}
	\rho_{ub}=k_{ub}e^{C(\theta_b-theta_{b,eq})}.
\end{equation}
We introduce a new model parameter $C$, the exponential unbinding constant, that controls this bias. To achieve trailing step bias, we define $C$ to be negative because the trailing $\theta_b$ tends to be less than the leading $\theta_b$ and  when $\theta_b$ is less than $\theta_{b,eq}$, the unbinding rate becomes large.

@@

The key difference between the works discussed in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state. Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk. However, they noticed that the unbinding process took a large amount of computation time relative to the total stepping time. They also noticed that the both bound configuration of dynein does not impact the final step length. We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.

@@

\subsection{Monte Carlo for Both Bound}
Since research and Waczak/Capek suggests that the dynein spends the majority of the stepping time in the both bound state, we can safely assume that the dynein equilibriates before unbinding. This inspired us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system. Typically, Monte Carlo methods are used to analyze equilibrium theromodynamics of fluids where a system of atoms can possess many different microstates. For this model, the dynein is the system and the different possible microstates are the many both bound configurations our model can achieve. However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values. The benefit of this method is the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics. Eventually, this will allow us to create probability distributions for important variables.

With the assumption of thermodyamic equilibrium during the both bound state, we can define the probability of dynein being in that configuration from a Boltzmann distribution and calculate the relative probability of unbinding for that specifc configuration by using a proportionality expression. That is, 
\begin{equation}
	P_{ub}\propto e^{-\beta E_{total}}.
\end{equation}
With this Boltzmann factor, we can also generate a partition function, 
\begin{equation} \label{eqn:partition}
	Z=\sum_{i}e^{-\beta E_{total,i}},
\end{equation}
where $i$ refers to the specific both bound configuration. In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well. The thermodynamic ensemble can then generate an ensemble of steps that can eventually produce smooth statictics. With the partition function defined in Equation (\ref{eqn:partition}), we can also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time. The equations to do so are all shown below in that order:
\begin{equation}
	\langle\rho_{ub, trail.}\rangle=\frac{\sum_{i}\rho_{ub, trail.} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, lead.}\rangle=\frac{\sum_{i}\rho_{ub, lead.} e^{-\beta E_{total,i}}}{Z}
\end{equation}
\begin{equation} \label{eqn:ProbTrail}
	\langle P_{ub, trail.}(L)\rangle = \frac{\langle\rho_{ub, trail.}\rangle}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle}
\end{equation}
\begin{equation}
	\langle t_{bb}(L) \rangle =\frac{1}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle},
\end{equation}
where $trail.$ and $lead.$ signifies a trailing or leading step.

>>>>

Despite dynein's complexity allowing its step to vary in both length and direction, we limit our model to one direction to eliminate the off-axis dimension when analyzing the forward stepping pattern of dynein. This would also simplify the asymmetry of the microtubule when the dynein is stepping either on the $\alpha$ or $\beta$ tubulin. We also simplify the stalk and linker to be massless because we are assuming the drag force to be much larger than the mass of the rods and domains. The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics. Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains abitrarily 10\% larger than experimental measurements.

\subsection{Domains as Angular Springs}
To best simulate the stretching and forward kicking motion of the power stroke, we define the domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$. This can be analogous to how humans walk, where the domains correspond to flexible joints when taking a step. Defining the domains as springs also allows us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law, 
\begin{equation}
    F_i=-c_i(\theta_i-\theta_{i,eq}),
\end{equation}
where $c_i$ is the spring constant, $\theta_i$ is angle corresponding to the $i^{th}$ domain, and $\theta_{i,eq}$ is the equilibrium angle in which biases the motion. Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy:
\begin{equation} \label{eqn:energy}
    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2.
\end{equation}
%Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e. $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains. 
This equation is used throughout the simulation to determine the total energy of our dynein at a given conformation.

\subsection{Two-State System}
According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step. However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity. Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.

@@

Similar to other simulations, the binding and unbinding process is governed by rate-limiting steps, where each process is associated with binding rates. These binding rates are model parameters defined by binding constants with units of probability per time. When the dynein is in the one bound state, the binding domain depends on two rebinding parameters: the affinity transition time ($t_a$) and the binding rate ($\rho_b$). We assume that the unbound binding domain can only bind when high affinity completely transitions into low affinity and when the domain is within a vertical range of the microtubule, i.e.
\begin{equation}
	t>t_a=\frac{1}{k_a}
\end{equation}
and
\begin{equation}
	\rho_b=k_b(1-H(r_{ub,y}-\epsilon)).
\end{equation} 
Here, $t$ is the total one bound time, $k_a$ is the affinity transition rate, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.

@@

To favor trailing steps, we define an angle dependent exponential factor within the binding domains and mathematically express this as,
\begin{equation}
	\rho_{ub}=k_{ub}e^{C(\theta_b-\theta_{b,eq})}.
\end{equation}
We introduce a new model parameter $C$, the exponential unbinding constant, that controls this bias. To achieve trailing step bias, we define $C$ to be negative because the trailing $\theta_b$ tends to be less than the leading $\theta_b$ and  when $\theta_b$ is less than $\theta_{b,eq}$, the unbinding rate becomes large.

@@

The key difference between the works in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state. In addition to the large both bound time mentioned earlier, they also noticed that the initial both bound configuration of the domains does not impact the stepping, giving a better incentive to apply a Monte Carlo approach. This new method of analyzing the both bound state will significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.

@@

\subsection{Monte Carlo for Both Bound}
Since dynein spends the majority of time in the both bound state, we can safely assume that the dynein equilibriates before unbinding. This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system. Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids where a system of atoms possess many different microstates. For this model, dynein is the system and the many possible both bound configurations is analogous to the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values. The enables the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics. Eventually, this allows us to create probability distributions for important variables.

With the assumption of thermodyamic equilibrium during the both bound state, we define the probability of a configuration from a Boltzmann distribution and calculate the relative unbinding probability for that configuration by using a proportionality expression. That is, 
\begin{equation}
	P_{ub}\propto e^{-\beta E_{total}}.
\end{equation}
With this Boltzmann factor, we can also generate a partition function, 
\begin{equation} \label{eqn:partition}
	Z=\sum_{i}e^{-\beta E_{total,i}},
\end{equation}
where $i$ refers to the specific both bound configuration. In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well. The thermodynamic ensemble then generates an ensemble of steps that can eventually produce smooth statictics. With the partition function defined in Equation (\ref{eqn:partition}), we also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time. The equations to do so are all shown below in that order:
\begin{equation}
	\langle\rho_{\textit{ub, trail.}}\rangle=\frac{\sum_{i}\rho_{\textit{ub, trail.}} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{\textit{ub, lead.}}\rangle=\frac{\sum_{i}\rho_{\textit{ub, lead.}} e^{-\beta E_{total,i}}}{Z}
\end{equation}
\begin{equation} \label{eqn:ProbTrail}
	\langle P_{\textit{ub, trail.}}(L)\rangle = \frac{\langle\rho_{\textit{ub, trail.}}\rangle}{\langle\rho_{\textit{ub, trail.}}\rangle + \langle\rho_{\textit{ub, lead.}}\rangle}
\end{equation}
\begin{equation}
	\langle t_{bb}(L) \rangle =\frac{1}{\langle\rho_{\textit{ub, trail.}}\rangle + \langle\rho_{\textit{ub, lead.}}\rangle},
\end{equation}
where $trail.$ and $lead.$ signifies a trailing or leading step.
